In this section I shall demonstrate that \textsc{EviL} is not compact by giving an example of an infinite set of formulae for which every finite subset is satisfiable while the entirety is not.

\begin{lemma}
Let $\tau : \Phi \to \mathcal{L}$ be defined as follows:
\begin{center}
\begin{minipage}{3in}
\begin{tabbing}
	$\tau(p) := $ \=$p \wedge \Pos\top \wedge$ \\
	\> $\Nec$ \= $(\neg p \wedge \Pos\top \wedge$\\
	\> \> $\Nec$ \= $(p \wedge \Pos p))$
\end{tabbing}
\end{minipage}
\end{center}
Every finite subset of $\tau[\Phi]$ is satisfiable, but not the entirety, which is infinite. 
\end{lemma}
\begin{proof}
That $\tau[\Phi]$ is infinite is immediate, as $\Phi$ was stipulated to be infinite. 

So let $S\subseteq \tau[\Phi]$ by finite.  We shall find a model that
satisfies $S$.  First observe that there is a
 finite $\Psi\subset
\Phi$ such that $S = \tau[\Psi]$.  Let $\{q,r,s\} \subseteq \Phi \; \bs
\; \Psi$ be
 three distinct letters - this can be done, since $\Phi \;
\bs \; \Psi$ is infinite.
  Let $\mathfrak{M} = \{\pr{a}{\{q\}},
\pr{b}{\{r\}}, \pr{c}{\{s\}} \}$, where 
\begin{align*}
a & := \Psi \cup \{s\} \\
b & := \{q \} \\
c & := \Psi \cup \{r\}
\end{align*}
 Using the same visualizations I introduced in \S\ref{contradictions},
 $\mathfrak{M}$ can  be visualized\footnote{While this situation
   presents itself like a Kripke model, I am not employing Kripke
   semantics.  The means in which one world accesses another is not by
   an accessibility relation, but rather through the sets of beliefs,
   which in this case are the sets ${q},{r},$ and ${s}$.} in Fig. \ref{fig:mod4}.  It is straightforward to 
check that $\mathfrak{M},( a,\{q\}) \VDash \tau(p)$ for all $p \in \Psi$.

	\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
	\begin{tikzpicture}[->,
         shorten >=3pt, shorten <= 3pt, 
         auto,node distance=4cm, semithick]
  \tikzstyle{state}=[draw=black, shape=rectangle]
  \tikzstyle{empt} = [draw=none,fill=none]
\begin{scope}
\node[state] (aA1) at (45:2.5) [] {$\pr{a}{\{q\}}$};
\node[empt] (aA2) at (165:2.5) {$\pr{b}{\{r\}}$};
\node[empt] (aA3) at (285:2.5) {$\pr{c}{\{s\}}$};
\path
(aA1) edge [->,bend right] node {} (aA2)
(aA2) edge [->,bend right] node {} (aA3)
(aA3) edge [->,bend right] node {} (aA1);
\end{scope}
\end{tikzpicture}
\caption{$\mathfrak{M},\pr{a}{\{q\}}\VDash \tau[\Psi]$}
   \label{fig:mod4}
\end{figure}
On the other hand, suppose there was some model $\mathfrak{N}$ such that $\mathfrak{N}, ( a, A) \VDash \tau(p)$ for all $p \in \Psi$.
This implies that $\mathfrak{N}, ( a, A) \VDash p$ for each $p \in
\Phi$.  Moreover, let $( b, B)\in\mathfrak{N}$ be such that $b \models A$ 
(one exists since by hypothesis $\mathfrak{N}, ( a, A)
\VDash \Pos p$).  By the semantics of $\tau(p)$, it is evident that
$\mathfrak{N}, ( b, B) \VDash \neg p$ and that there's a $( c, C)\in\mathfrak{N}$
such that $c \models B$ and $\mathfrak{N},( c,C )
\VDash p \wedge \Pos p$.  But then from this it must be that $a$ and
$c$ both contain exactly the same sentence letters, so $a = b$ which means that
$a \models B$ as well, since $B \subseteq
\mathcal{L}_0$ (as per the grammar restriction).  However it cannot be that
$\mathfrak{N},( a,A ) \VDash \Pos p$ since $\mathfrak{N},( a,A )
\VDash \Nec \neg p$, which follows from the assumption that $\mathfrak{N},( a,A )
\VDash \tau(p)$. 
Thus it is impossible that $\mathfrak{N},( a, A) \VDash \tau[\Phi]$. $\lightning$
\end{proof}

The above argument illustrates that while \textsc{EviL} semantics
present themselves as similar to the traditional Kripke Semantics for modal
logic, they aren't the same.  If for some reason two world-pairs
$(a,A)$ and $(b,B)$ make true the same sentence letters, then $a=b$,
and then for any $C \subseteq \mathcal{L}_0$, we have that $a \models
C$ if and only if $b \models C$. This is crucial - even though
\textsc{EviL} is modal, it has no accessibility relations; the role of
accessibility relations is instead picked up by sets of beliefs $C$. 
Since my initial design considerations for \textsc{EviL} demanded a
grammar restriction, to ensure the semantics were well-defined,
an unusual failure of compactness manifests itself.

My failure of compactness, while a fairly basic result in the model
theory of \textsc{EviL}, has far reaching consequences for the model
theory of \textsc{EviL}.  As a consequence, there is
no hope of achieving completeness using infinitary Lindenbaum
constructions that are typically employed in modal logic, such as is
done in \citep[][chapter 4]{blackburn_modal_2001}, for instance.
Hence the completeness theorem for \textsc{EviL} presented in \S\ref{army-of-darkness}
will necessarily have to be finite in nature.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "evil_philosophy"
%%% End: 
