In this section we provide a complete axiomatization of
multi-agent \textsc{EviL}.  In addition to axiomatics, we shall also
look at subsystems and supersystems of \textsc{EviL}, and provide
complexity bounds on \textsc{EviL} decision procedures. 

We have organized this section in the following manner:
\begin{description}
 \item[\S\ref{evil-axioms}] We first present a sound axiom
   system for \textsc{EviL}.

 \item[\S\ref{abstraction}] Next, we give a definition of the
   class of \emph{partly \textsc{EviL}} Kripke structures.  

   We then reveal that \textsc{EviL} is sound and strongly complete
   for the class of partly \textsc{EviL} structures. 
   Completeness rests on the observation that the
   axioms of \textsc{EviL} are all in the \emph{Sahlqvist fragment},
   or have obvious meanings in terms of the traditional canonical
   model construction for Modal Logic.
   This abstract completeness for \textsc{EviL} can be understood as
   an elementary application of van Benthem's 
   \emph{correspondence theory} for modal logic.

\item[\S\ref{completely-evil}]  In this section we recall the definition of an
  \emph{\textsc{EviL} Kripke structure}, as we gave in Definition
  \ref{evil-kripke-structures} from \S\ref{kripke}, and show that
  every \emph{partly \textsc{EviL}} Kripke structure may be
  ``completed'' by constructing a bisimilar \emph{\textsc{EviL}} 
   structure.

   This has, as a consequence, that \textsc{EviL} is complete for
   \textsc{EviL} Kripke structures.

\item[\S\ref{taking-stock}]  In this section, we discuss why the abstract
  completeness proof developed in the previous sections, while
  important, is not adequate in light of the developments in
  \S\ref{basic-evil} and the intuitions we saw in that section.  We
  shall sketch what further needs to be shown to give the desired
  completeness theorem for \textsc{EviL}.

\item[\S\ref{small-model}]  In this section we show that
  \textsc{EviL} has a small model property for \emph{partly
    \textsc{EviL}} Kripke structure. This is accomplished by constructing
     a Kripke structure consisting of finite maximally
     consistent sets in the manner of the Fischer-Ladner closure style
     completeness proof of PDL 
     \cite[chapter 4, pgs. 241--248]{blackburn_modal_2001}.
We also discuss how our results give rise to complexity observations for
  the \textsc{EviL} decision problem.

% \item[\S\ref{decidability}] 
%    From our construction in the previous section, we obtain a decidability
%    result for \textsc{EviL}, and provide upper and lower bounds on the
%    complexity of the \textsc{EviL} decision problem.

  \item[\S\ref{islands}] In this section, we introduce the concept of an
    \emph{island}, which are special equivalence classes for
    \textsc{EviL} structures.  
   We shall prove several properties, which take the
    form of various irreducibilities. 

\item[\S\ref{translation}]Following the proof of Proposition
  \ref{translation-sketch} in \S\ref{sketch}, we shall show that every
  finite \textsc{EviL} Kripke structure is \emph{(almost)-homomorphic} to another,
  \textsc{EviL} structure we shall call $\ipent$, provided that we have an
  infinite number of letters in $\Phi$.  
  We shall show that there is a map $\kl$ of worlds in $\mathbb{M}$ to
  worlds in $\ipent$ that preserves formulae in a language
  $\mathcal{L}(\Psi,\mathcal{A})$ where 
$\Psi \subseteq_\omega \Phi$.

  The construction of $\ipent$ shall make use of the island structures introduced
  in the previous section, and here we will also introduce the concept of
  \emph{names} and \emph{surnames}.

We have, as a consequence of the above, we shall be able to show that
$\textsc{EviL}$ is weakly complete for $\textsc{EviL}$ structures.

  % \item[\S\ref{skarmy-of-darkness}]  In this section, we employ our
  %   previous results to remark that \textsc{EviL} is weakly complete for
  %   \textsc{EviL} models.

\item[\S\ref{taking-stockII}]  In this section, we once again pause to
  take stock of the results we have established in previous sections.
  Here we discuss the relationship between the abstract
  completeness we have previously established and our concrete 
  completeness.

  \item[\S\ref{subsystems}] We next introduce two
    subsystems of \textsc{EviL}, corresponding to the $\BP$ and $\BM$
    only fragments. We briefly go over the completeness theorems and
    the small model property for these systems, as well as
    decidability results.  In each case, a special
    bisimulation theorem is in order to achieve completeness.

  \item[\S\ref{supersystems}] We provide an extension to
    \textsc{EviL} and its subsystems, introducing the universal
    modality $U$. We sketch completeness and the finite model
    property, and mention how translation may be extended to this
    system.

 \item[\S\ref{lattice}]  In this section we give a lattice of
   \textsc{EviL} systems, and discuss the known complexity bounds of
   various levels of this lattice.
\end{description}

%\subsection{Failure of Compactness}
%\label{non-compactness}
%\input{evil_noncompactness.tex}

\subsection{Axioms of \textsc{EviL}}\label{evil-axioms}
\input{evil_axiom_systems.tex}

\subsection{Partly \textsc{EviL} Kripke Structures \& Strong Completeness}\label{abstraction}\label{partly-evil-strong-soundness-and-completeness}
\input{partly-evil-models.tex}

\subsection{Bisimulation \& \textsc{EviL} Strong Completeness}\label{completely-evil}\label{Abstract-Completeness}
\input{bisimulation.tex}

\subsection{Taking Stock I}\label{taking-stock}
\input{taking-stock.tex}

\subsection{Small Model Construction}\label{small-model}
\input{small-model.tex}

\subsection{Islands}\label{islands}
\input{islands.tex}

\subsection{Translation \& \textsc{Evil} Completeness}
\label{translation}
\input{translation.tex}
% \subsection{\textsc{EviL} Completeness}\label{skarmy-of-darkness} 
% \input{completeness.tex}

\subsection{Taking Stock II}\label{taking-stockII}
\input{taking-stockII.tex}

\subsection{Subsystems of \textsc{EviL}}\label{subsystems}
\input{subsystems.tex}

\subsection{Universal Modality}\label{supersystems}
\input{universal.tex}

\subsection{Lattice of Logics \& Complexity}\label{lattice}\label{conservative-extension}
\input{lattice.tex}

%\subsection{Completeness}\label{conservative-extension}

%\subsection{Conservativity, Decidability \& Complexity}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "evil_philosophy"
%%% End: 
